### 2023-03-30 resilience-safe-up.tex
up

\subsection{Case: $\Safe=\uparrow \Safe$ and $\Bad = ... $.}

\alain{2 clos par le haut ont une intersection non vide....}

Since we impose $\Bad \cap \Safe = \emptyset$, we cannot have as an hypothesis
both $\Safe = \uparrow \Safe$ and $\Bad = \uparrow \Bad$. To approximate a case
of double upward closure, we consider a case where $\Bad$ is as upward-closed
as it can be without intersecting with $\Safe$,
i.e. 
such that there exists an upward closed set $U$
such that $\Bad = U \setminus \Safe$.
Morally speaking ... [].

\begin{theorem}\label{up-up}
The resilience problem is decidable for effective WSTS with effective pred-basis, $\Safe=\uparrow \Safe$
and $\Bad= U \setminus \Safe$.

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective pred-basis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=U \setminus \Safe$.
\end{corollary}

\begin{theorem}\label{k-up-up}
The % three %uniform 
$k$-resilience problem is decidable for WSTS with effective pred-basis, strong %upward-
compatibility, $\Safe=\uparrow \Safe$
and $\Bad=U \setminus \Safe$.
%	and \Bad is upward closed or downward closed.
\end{theorem}

@@

>>>>

@@

\subsection{Case: $\Safe=\uparrow \Safe$ and $\Bad = \uparrow U \setminus \Safe $.}

% \alain{2 clos par le haut ont une intersection non vide....}

Since we impose $\Bad \cap \Safe = \emptyset$, we cannot have as an hypothesis
both $\Safe = \uparrow \Safe$ and $\Bad = \uparrow \Bad$. To approximate a case
of double upward closure, we consider a case where $\Bad$ is as upward-closed
as it can be without intersecting with $\Safe$,
i.e. 
such that there exists an upward-closed set $U$
such that $\Bad = U \setminus \Safe$.
Morally speaking ... [].

\begin{theorem}\label{up-up}
The resilience problem is decidable for effective WSTS with effective pred-basis, $\Safe=\uparrow \Safe$
and $\Bad= U \setminus \Safe$ with $U = \uparrow U$.

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective pred-basis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=U \setminus \Safe$ with $U = \uparrow U$.
\end{corollary}

\begin{theorem}\label{k-up-up}
The % three %uniform 
$k$-resilience problem is decidable for WSTS with effective pred-basis, strong %upward-
compatibility, $\Safe=\uparrow \Safe$
and $\Bad=U \setminus \Safe$  with $U = \uparrow U$.
%	and \Bad is upward closed or downward closed.
\end{theorem}
